Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-01-04 ThesisJP/Introduction/introduction.tex
Small layout adjustments

\subsubsection{Paper no. 1:\\
An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}

@@

\subsubsection{Paper no. 2:\\
Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}

@@

\section{Publication list}

\subsubsection{Papers included in the thesis}
\begin{enumerate}
	\item J. I. Buskenes, J. P. \AA{}sen, C.-I. C. Nilsen and A. Austeng, "An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging", {\it Submitted for review to IEEE Transactions on Oceanic Engineering}.
	\item 
\end{enumerate}

\subsubsection{Conference proceedings}
\begin{enumerate}
	\item 
	\item 
\end{enumerate}

\subsubsection{Presentations and abstracts}
\begin{enumerate}
	\item
\end{enumerate}

>>>>

\subsubsection{Paper I:\\
An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}

@@

\subsubsection{Paper II:\\
Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}

@@
